Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-12-01 paper/paper-mainfile.tex
label tikz figures
some changes

%
% user import packages
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{xcolor}
\usepackage{booktabs} 
\usepackage[ruled, noend, linesnumbered]{algorithm2e}  
\usepackage{csquotes}
\usepackage{subcaption}
\usepackage{amssymb} 
\usepackage{tikz}
\usetikzlibrary{aiplans}

@@

\section{Inference of Preconditions and Effects}
\input{03--linearization-ground.tex}

@@

\begin{algorithm}[h]
	\caption{Calculation of linearized methods}
	\label{alg:Algorithm1}
	\KwData{$(F, T_P, T_C, \delta, M)$}
	\KwResult{$(F, T_P, T_C, \delta, M)$}

	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
	{
		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
		$G \gets \singlePrec$ \\
		\label{alg:StartBuildGraph}
		\For{a $\in$ F}{  
			\For{$t \in T_m$}{
				\For{$t' \in T_m$}{
					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
				}
			} 
			\label{alg:EndBuildGraph}	
		}	
		\label{alg:StartCycleBreak}
		\While{$G$ has cycles in it}{
			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
		}
		\label{alg:EndCycleBreak}
		$\prec'$ = Any linearization of $G$ \\
		\label{alg:TopSort}
		$m' = (tasks(m), \prec', \alpha(t))$ \\
		$M' = M' \cup  \{m'\}$ \\

	}
	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
\end{algorithm}

>>>>

%
% user import packages
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{xcolor}
\usepackage{booktabs} 
% \usepackage[ruled, noend, linesnumbered]{algorithm2e}  
\usepackage{csquotes}
\usepackage{subcaption}
\usepackage{amssymb} 
\usepackage{mathbbol}
\usepackage{tikz}
\usetikzlibrary{aiplans}

@@

\section{Linearizing Grounded HTN Problems}
\input{03--linearization-ground.tex}

@@

\begin{algorithm}
	\input{alg-linearization.tex}
	\caption{Lineraizing a method.}
	\label{alg:Algorithm1}
\end{algorithm}

% \begin{algorithm}[h]
% 	\caption{Calculation of linearized methods}
% 	\label{alg:Algorithm1}
% 	\KwData{$(F, T_P, T_C, \delta, M)$}
% 	\KwResult{$(F, T_P, T_C, \delta, M)$}

% 	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
% 	{
% 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
% 		$G \gets \singlePrec$ \\
% 		\label{alg:StartBuildGraph}
% 		\For{a $\in$ F}{  
% 			\For{$t \in T_m$}{
% 				\For{$t' \in T_m$}{
% 					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
% 					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
% 					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
% 					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
% 				}
% 			} 
% 			\label{alg:EndBuildGraph}	
% 		}	
% 		\label{alg:StartCycleBreak}
% 		\While{$G$ has cycles in it}{
% 			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
% 		}
% 		\label{alg:EndCycleBreak}
% 		$\prec'$ = Any linearization of $G$ \\
% 		\label{alg:TopSort}
% 		$m' = (tasks(m), \prec', \alpha(t))$ \\
% 		$M' = M' \cup  \{m'\}$ \\

% 	}
% 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
% \end{algorithm}
